---
title: "Measurement Error Correction Simulation"
author: "Klaus Frieler"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("ME_simulator.R")
```

## General

This R project allows to simulate four different types  of measurement error (classical, differential, heteroscedastic, systematic) and how it effects the coefficient estimates in a simple linear regression model with two predictors. Additional, it presents  four different methods for correcting the measurement error (ME): A Latent Variable Model approach (LV), multiple imputation (MI), SIMEX (SMX), and a simple outlier exclusion (OE), and of course without any correction. We further have two scenarios, one where the ME only affects one predictor (scenario 1) and one where it affects both (scenario 2).

To this end, we provide a R6 class, `ME_simulator`. To use this, first create an object of that class, with a bunch of parameters (whereall have reasonable defaults). For example, here is scenario 2 simulation

```{r creation}
mesim <- ME_simulator$new(scenario = 2, 
                          n_batch = 1, 
                          error_types = c("classical"),
                          measurement_errors = c(1),
                          me_diffs = c(0),
                          n_sample = 50)
print(mesim)
```

It set ups a simulation object with one batch (repetition of simulations), only classical error, one measurement error (expressed as variance ratio) and no ME differences, which would simulate a mismatch of ME estimation, which enters the correction algorithms, and true ME, expressed as differences. For each simulated batch, we  use a sample size of `n_sample = 50`.

After the object is created, we can run the simulations by using the object method `run.`

```{r running}
mesim$run()
```
Per default, the verbosity is on, so we get a bunch of messages to watch the simulations going on. Note that this can take a long time, depending on the settings, With only single batch and one ME difference, this example will take  a reasonable short time to run.

After the run, the results are stored in the `mesim` object, and can be accessed directly, as well as some summary stats of the simulations. 

```{r results}
mesim$results
mesim$result_stats

```

There is also a flexible plotting option with the `diagnostics` member function. This will plot a metric (of your choosing) by correction method and error type over different ME, by default, but can be very flexibly configured.


```{r plot}
stats <- mesim$diagnostics(alpha = .7)
```

The object can also be conveniently be saved and restored.

```{r saving}
mesim$save("my_sim.rds")

```

## Running simulations
To reproduce our simulations, you need to source ``simulations_main.R`` then type

```{r run_simulations }
source("simulations_main.R")
#not run 
#run_simulations()
```

This will take a while and save all created simulations in the sub-folder ``simulations``. These can reloaded, once the simulation have been run with 

```{r load_simulations }
load_simulations()
scenario1_n_50$diagnostics(max_se = .1)
```
which will load and add all simulations objects in the `` simulations`` folder to the global workspace.

Have fun!